Heuristics and Really Hard Instances for Subgraph Isomorphism Problems

### 2016-04-12 paper/paper.tex
Scale-free
Finer data

What if we alter the edge probabilities for both the pattern graph and the target graph?  In the top
row of \cref{figure:non-induced} we show the satisfiability phase transition for the non-induced
variant, for patterns of order 10, 20 and 30, targets of order 150, and varying pattern (x-axis)
and target (y-axis) edge probabilities. Each axis runs over 51 edge probabilities, from 0 to 1 in
steps of 0.02; for each of these 2601 points, we generate ten random instances. The colour denotes
the proportion of these instances which were found to be satisfiable.  Inside the orange region, at
the bottom right of each plot, every instance is unsatisfiable---here we are trying to find a dense
pattern in a sparse target. In the purple region, at the top left, every instance is
satisfiable---we are looking for a sparse pattern in a dense target (which is easy, since we only
have to preserve adjacency, not non-adjacency). The white band between the regions shows the
location of the phase transition: here, roughly half the instances are satisfiable. (We discuss the
black line below.)

@@

In future work, we intend to repeat the experiments using other random models, including bounded and
regular degree. We will also look at dynamic heuristics, and switching pattern and target heuristics
independently. Finally, we intend to investigate whether variance can be calculated efficiently
enough to give better predictions for very sparse or dense pattern graphs.

>>>>

What if we alter the edge probabilities for both the pattern graph and the target graph?  In the top
row of \cref{figure:non-induced} we show the satisfiability phase transition for the non-induced
variant, for patterns of order 10, 20 and 30, targets of order 150, and varying pattern (x-axis) and
target (y-axis) edge probabilities. Each axis runs over 101 edge probabilities, from 0 to 1 in steps
of 0.01, except for the VF2 row which uses steps of 0.02. For each of these points, we generate ten
random instances. The colour denotes the proportion of these instances which were found to be
satisfiable.  Inside the orange region, at the bottom right of each plot, every instance is
unsatisfiable---here we are trying to find a dense pattern in a sparse target. In the purple region,
at the top left, every instance is satisfiable---we are looking for a sparse pattern in a dense
target (which is easy, since we only have to preserve adjacency, not non-adjacency). The white band
between the regions shows the location of the phase transition: here, roughly half the instances are
satisfiable. (We discuss the black line below.)

@@

In future work, we intend to repeat the experiments using other random models, including bounded,
regular degree, and scale-free. We will also look at dynamic heuristics, and switching pattern and
target heuristics independently. Finally, we intend to investigate whether variance can be
calculated efficiently enough to give better predictions for very sparse or dense pattern graphs.
